---
title: "In Class Exercise 04"
editor: visual
format:
  html:
    code-fold: true
    code-summary: "Show the code"
    warning: false
    message: false
author: "Shi Chee Liang"
date: 02 February 2023
date-modified: "`r Sys.Date()`"
---

## Visualising Interactive elements

### **Importing and preparing the Data Set**

#### **loading packages**

Load the required packages.

```{r}
pacman::p_load(tidyverse, DT, patchwork, plotly, ggstatsplot)
```

Load the Data Set

```{r}
exam_data <- read_csv("data/Exam_data.csv")
```

###  Visualise with plot_ly

```{r}
plot_ly(data = exam_data, 
        x = ~ENGLISH, 
        y = ~MATHS, 
        color = ~RACE)
```

### Visualise using ggplotly

```{r}
p <- ggplot(data=exam_data, 
            aes(x = MATHS,
                y = ENGLISH)) +
  geom_point(dotsize = 1) +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100))
ggplotly(p)
```

### Visualise with ggstatsplot

```{r}
ggbetweenstats(
  data = exam_data,
  x = GENDER, 
  y = MATHS,
  type = "np",
  messages = FALSE
)
```

```{r}
ggscatterstats(
  data = exam_data,
  x = MATHS,
  y = ENGLISH,
  marginal = TRUE,
  )
```

## Visualising Models

### **Importing and preparing the Data Set**

#### **loading packages**

```{r}
pacman::p_load(readxl, performance, parameters, see, gtsummary)
```

#### Load the Data Set

```{r}
car_resale <- read_xls("data/ToyotaCorolla.xls", 
                       "data")
```

### Multiple Regression Model using lm()

```{r}
model <- lm(Price ~ Age_08_04 + Mfg_Year + KM + 
              Weight + Guarantee_Period, data = car_resale)
model
```

### Model Diagnostic: checking for multicolinearity:

```{r}
check_c <- check_collinearity(model)
plot(check_c)
```

### Model Diagnostic: checking normality assumption

```{r}
model1 <- lm(Price ~ Age_08_04 + KM + 
              Weight + Guarantee_Period, data = car_resale)
```

```{r}
check_n <- check_normality(model1)
```

```{r}
plot(check_n)
```

### Visualizing the uncertainty of point estimates: ggplot2 methods

```{r}
my_sum <- exam_data %>%
  group_by(RACE) %>%
  summarise(
    n=n(),
    mean=mean(MATHS),
    sd=sd(MATHS)
    ) %>%
  mutate(se=sd/sqrt(n-1))
```

drawing

```{r}
ggplot(my_sum) +
  geom_errorbar(
    aes(x=RACE, 
        ymin=mean-se, 
        ymax=mean+se), 
    width=0.2, 
    colour="black", 
    alpha=0.9, 
    size=0.5) +
  geom_point(aes 
           (x=RACE, 
            y=mean), 
           stat="identity", 
           color="red",
           size = 1.5,
           alpha=1) +
  ggtitle("Standard error of mean 
          maths score by rac")
```
